---
name: Ronald J. Yurko, Jr.
position: "Curriculum Vitae"
address: "Department of Statistics & Data Science, Carnegie Mellon University"
email: "ryurko@andrew.cmu.edu"
www: stat.cmu.edu/\textasciitilde ryurko/
twitter: Stat_Ron
github: ryurko
headcolor: 00008b
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(here)
```

```{r init_education, include = FALSE}
education_raw <- read_csv(here("data", "education.csv"))
education <- education_raw %>% 
  mutate(years = ifelse(!is.na(end_year),
                       paste0(start_year, "-", end_year),
                       paste0(start_year, "-", "Present")),
         degree = paste0(degree, " in ", program))
```


```{r init_publications, include = FALSE}
papers_raw <- read_csv(here("data", "publications.csv")) #%>%
# Comment out with 0 preprints
#  bind_rows(read_csv(here("data", "preprints.csv")))
papers <- papers_raw %>% 
  # Specify the release text based on if the status == "Published"
  mutate(release = ifelse(status == "Published",
                          pub_year,
                          status),
         # If the status is forthcoming then make the release combined:
         release = ifelse(status == "Forthcoming", 
                          paste0(status, " (", pub_year, ")"), release),
         # Now relevel the status so that in goes from in progress, under review
         # Forthcoming to  Published:
         status = fct_relevel(status, "In progress", "Under review", 
                              "Forthcoming", "Published"),
         # Create the line providing the url for the paper:
         url_location = ifelse(!is.na(url),
                               paste0(website, ": ", url),
                               NA),
         # Create a status_order variable that will be used just to figure out
         # which is the first paper in a group:
         status_order = ifelse(!is.na(pub_year), paste(status, pub_year, "-"),
                               status)) %>%
  # Now arrange by the status then year:
  arrange(status, desc(status_order)) %>%
  # Now group by the status_order to generate an ordering so the lefthand labels are
  # not repeated:
  group_by(status_order) %>%
  mutate(status_order_i = 1:n(),
         display_label = ifelse(status_order_i == 1, as.character(release), "")) %>%
  ungroup()
  
```

```{r init_misc-articles, include = FALSE}
misc_articles_raw <- read_csv(here("data", "misc_articles.csv")) 
misc_articles <- misc_articles_raw %>% 
  # Specify the release text based on if the status == "Published"
  mutate(release = ifelse(status == "Published",
                          pub_year,
                          status),
         # If the status is forthcoming then make the release combined:
         release = ifelse(status == "Forthcoming", 
                          paste0(status, " (", pub_year, ")"), release),
         # Now relevel the status so that in goes from in progress, under review
         # to published:
         status = factor(status, 
                         levels = c("In progress", "Under review", "Published")),
         # Create the line providing the url for the paper:
         # url_location = ifelse(!is.na(url),
         #                       paste0(website, ": ", url),
         #                       NA),
         # Create a status_order variable that will be used just to figure out
         # which is the first paper in a group:
         status_order = ifelse(!is.na(pub_year), paste(status, pub_year, "-"),
                               status)) %>%
  # Now arrange by the status then year:
  arrange(status, desc(status_order)) %>%
  # Now group by the status_order to generate an ordering so the lefthand labels are
  # not repeated:
  group_by(status_order) %>%
  mutate(status_order_i = 1:n(),
         display_label = ifelse(status_order_i == 1, as.character(release), "")) %>%
  ungroup()
```

```{r init_presentations, include = FALSE}
presentations_raw <- read_csv(here("data", "presentations.csv")) 
presentations <- presentations_raw %>% 
  # Now arrange by the type then year:
  arrange(presentation_type, desc(year)) %>%
  # Now group by the presentation_type to generate an ordering so the lefthand labels are
  # not repeated:
  group_by(presentation_type, year) %>%
  mutate(type_order_i = 1:n(),
         display_label = ifelse(type_order_i == 1, as.character(year), "")) %>%
  ungroup()

```


```{r init_software, include = FALSE}
software <- read_csv(here("data", "software.csv")) %>%
    # Specify the release text based on if the status == "Published"
  mutate(# Create the line providing the url for the paper:
         url_location = ifelse(!is.na(url),
                               paste0(website, ": ", url),
                               NA)) %>%
  # Now arrange by the status then year:
  arrange(pub_year) %>%
  # Now group by the status_order to generate an ordering so the lefthand labels are
  # not repeated:
  group_by(pub_year) %>%
  mutate(pub_year_i = 1:n(),
         display_label = ifelse(pub_year_i == 1, as.character(pub_year), "")) %>%
  ungroup()
  
```


```{r init_teaching, include = FALSE}
teaching_raw <- read_csv(here("data", "teaching.csv")) 
teaching <- teaching_raw %>% 
  # First make the semester a factor with specified order:
  mutate(semester = factor(semester, 
                           levels = c("Spring", "Summer", "Fall"))) %>%
  arrange(desc(year), desc(semester)) %>%
  mutate(class_order = 1:n()) %>%
  # Need to summarize each class label in terms of the semesters and years:
  group_by(teaching_id, semester) %>%
  mutate(semester_years = paste(sort(unique(year)), collapse = ", "),
         semester_label = paste(semester, semester_years, sep = ": ")) %>%
  ungroup() %>%
  group_by(teaching_id) %>%
  summarize(title = first(title),
            location = first(location),
            notes = first(notes),
            role = first(role),
            semester_summary = paste(unique(semester_label), collapse = ", "),
            display_label = ifelse(length(unique(year)) > 1,
                                          paste0(min(year), " - ", max(year)),
                                   as.character(unique(year))),
            class_order = first(class_order)) %>%
  arrange(class_order) 

```

```{r init_research_experience, include = FALSE}
research_experience <- read_csv(here("data", "research_experience.csv")) %>%
  mutate(years = case_when(
                   is.na(end_year) ~ paste0(start_year, "-Present"),
                   start_year == end_year ~ as.character(start_year),
                   TRUE ~ paste0(start_year, "-", end_year)),
         advised_by = paste0("Advised by: ", advisors))
```

```{r init_industry, include = FALSE}
industry_experience <- read_csv(here("data", "industry.csv")) %>%
  mutate(years = case_when(
                   is.na(end_year) ~ paste0(start_year, "-Present"),
                   start_year == end_year ~ as.character(start_year),
                   TRUE ~ paste0(start_year, "-", end_year)),
         display_location = paste(department, company, location, sep = ", "))
```

```{r init_fellowships_grants, include = FALSE}
fellowships_grants <- read_csv(here("data", "fellowship_funding.csv")) %>%
  arrange(desc(start_year)) %>%
  mutate(years = case_when(
                   is.na(end_year) ~ paste0(start_year, "-Present"),
                   start_year == end_year ~ as.character(start_year),
                   TRUE ~ paste0(start_year, "-", end_year)))

```

```{r init_honors_awards, include = FALSE}
honors_awards <- read_csv(here("data", "honors_awards.csv")) %>%
  arrange(desc(year))

```

```{r init_professional_service, include = FALSE}
professional_service <- read_csv(here("data", "professional_service.csv")) %>%
    mutate(years = case_when(
                   is.na(end_year) ~ paste0(start_year, "-Present"),
                   start_year == end_year ~ as.character(start_year),
                   TRUE ~ paste0(start_year, "-", end_year))) %>%
  arrange(desc(start_year))
```

```{r init_workshops, include = FALSE}
workshops_attended <- read_csv(here("data", "workshops_attended.csv")) %>%
  arrange(desc(year))

```

```{r init_societies, include = FALSE}
professional_societies <- read_csv(here("data", "professional_societies.csv")) %>%
  arrange(society)
```

```{r init_computing_skills, include = FALSE}
computing_skills <- read_csv(here("data", "computing_skills.csv")) %>% 
  mutate(level = factor(level,
                        levels = c("Expert", "Proficient", "Intermediate",
                                   "Beginner"))) %>%
  group_by(level) %>%
  summarize(languages = paste(languages, collapse = ", ")) %>%
  arrange(level)
```

```{r init_activities, include = FALSE}
activities <- read_csv(here("data", "activities.csv")) %>%
  mutate(years = case_when(
                   is.na(end_year) ~ paste0(start_year, "-Present"),
                   start_year == end_year ~ as.character(start_year),
                   TRUE ~ paste0(start_year, "-", end_year))) %>%
  arrange(desc(start_year))
```


# Education

```{r education}
education %>%
  detailed_entries(
    what = degree,
    when = years,
    with = school,
    why = notes
  )
```

# Publications

```{r publications}
#bibliography_entries(here("data", "publications.bib"))
# add 'and Preprints' above if there are preprints to include
papers %>%
  detailed_entries(what = title,
                   with = authors,
                   where = journal,
                   when = display_label,
                   why = url_location)
```

# Presentations

## Invited Talks

```{r}
presentations %>%
  filter(presentation_type == "invited_talk") %>%
  detailed_entries(what = title,
                   with = author_notes,
                   where = conference,
                   when = display_label,
                   why = more_info)
```


## Contributed Talks

```{r}
presentations %>%
  filter(presentation_type == "contributed") %>%
  detailed_entries(what = title,
                   with = author_notes,
                   where = conference,
                   when = display_label,
                   why = more_info)
```


## Conference Poster Presentations

```{r}
presentations %>%
  filter(presentation_type == "poster") %>%
  detailed_entries(what = title,
                   with = author_notes,
                   where = conference,
                   when = display_label,
                   why = more_info)
```

## Electronic Poster Presentations

```{r}
presentations %>%
  filter(presentation_type == "eposter") %>%
  detailed_entries(what = title,
                   with = author_notes,
                   where = conference,
                   when = display_label,
                   why = more_info)
```

# Miscellaneous Articles

```{r misc-articles}
misc_articles %>%
  detailed_entries(what = title,
                   with = authors,
                   where = journal,
                   when = display_label,
                   why = more_info)
```


# Software

## R Packages

```{r}
software %>%
  detailed_entries(what = title,
                   with = authors,
                   when = display_label,
                   why = url_location)
```


# Teaching Experience

## Courses Taught at Carnegie Mellon 

```{r}
teaching %>%
  filter(role == "course_instructor") %>%
  detailed_entries(what = title,
                   when = display_label,
                   with = semester_summary,
                   why = notes)
```

## Courses Served as Teaching Assistant at Carnegie Mellon

```{r}
teaching %>%
  filter(role == "course_ta") %>%
  detailed_entries(what = title,
                   when = display_label,
                   with = semester_summary,
                   why = notes)
```

## Courses Served as Grader at Carnegie Mellon

```{r}
teaching %>%
  filter(role == "course_grader") %>%
  detailed_entries(what = title,
                   when = display_label,
                   with = semester_summary,
                   why = notes)
```

## Workshops Taught

```{r}
teaching %>%
  filter(role == "workshop_instructor") %>%
  detailed_entries(what = title,
                   when = display_label,
                   why = notes)
```

# Research Experience

## Research Assistant at Carnegie Mellon

```{r}
research_experience %>%
  filter(type == "ra") %>%
  arrange(desc(start_year)) %>%
  detailed_entries(what = role_title,
                   when = years,
                   with = advised_by,
                   where = project_title)
```


## Other Research Experience at Carnegie Mellon

```{r}
research_experience %>%
  filter(type == "other") %>%
  arrange(desc(start_year)) %>%
  detailed_entries(what = role_title,
                   when = years,
                   with = advised_by,
                   where = project_title)
```


# Industry Experience

## Part-time

```{r}
industry_experience %>%
  filter(type == "part") %>%
  arrange(desc(start_year)) %>%
  detailed_entries(what = role,
                   when = years,
                   where = display_location)
```


## Full-time

```{r}
industry_experience %>%
  filter(type == "full") %>%
  arrange(desc(start_year)) %>%
  detailed_entries(what = role,
                   when = years,
                   where = display_location)
```

## Internships

```{r}
industry_experience %>%
  filter(type == "intern") %>%
  arrange(desc(start_year)) %>%
  detailed_entries(what = role,
                   when = years,
                   where = display_location)
```


# Fellowships and Funding

```{r}
fellowships_grants %>%
  detailed_entries(what = title,
                   when = years)
```

# Honors and Awards

```{r}
honors_awards %>%
  detailed_entries(what = title,
                   when = year,
                   with = extra_info,
                   where = from)
```

# Professional Service

## Organization

```{r}
professional_service %>%
  filter(type == "organize") %>%
  detailed_entries(what = service_title,
                   where = service_for,
                   why = service_info,
                   when = years)
```

## Journal Reviewer

```{r}
professional_service %>%
  filter(type == "journal_review") %>%
  summarize(journals = paste0(service_for, collapse = ", ")) %>%
  detailed_entries(what = journals)
```

## Department Service

```{r}
professional_service %>%
  filter(type == "dept_service") %>%
  detailed_entries(what = service_title,
                   where = service_for,
                   when = years)
```

## University Service

```{r}
professional_service %>%
  filter(type == "univ_service") %>%
  detailed_entries(what = service_title,
                   where = service_for,
                   when = years)
```

# Workshop Participation

```{r}
workshops_attended %>%
  detailed_entries(what = workshop_name,
                   when = year,
                   where = location)
```

# Professional Societies

```{r}
professional_societies %>%
  detailed_entries(what = society)
```

# Computing Skills

```{r}
computing_skills %>%
  detailed_entries(what = languages, 
                   when = level)
```

# Activities

## Team Sports

```{r}
activities %>%
  filter(type == "team_sports") %>%
  detailed_entries(what = activity,
                   when = years,
                   why = activity_info)
```

## Volunteering

```{r}
activities %>%
  filter(type == "volunteering") %>%
  detailed_entries(what = activity,
                   when = years,
                   why = activity_info)
```

## Charity Runs

```{r}
activities %>%
  filter(type == "runs") %>%
  detailed_entries(what = activity,
                   when = years,
                   why = activity_info)
```


